---
title: "Quarto Feature Test"
order: 2
---

```{r include=FALSE}
```

This document tests various Quarto features to ensure they render correctly. It focuses on callouts, grouped tabsets, figures, tables, Mermaid diagrams, and code blocks (with and without execution).

## Callouts

We will test different types of callouts.

::: {.callout-note}
This is a *standard note callout*. It should render as a note.
:::

::: {.callout-tip}
This is a **tip callout**. It should render as a tip, distinguishable from a note.
:::

## Grouped Tabsets

These tests ensure grouped tabsets render correctly and are interactive.

::: {.panel-tabset group="test-tabset"}

## Tab 1

Foo

## Tab 2

Bar

## Tab 3

Baz

:::

And another one

::: {.panel-tabset group="test-tabset"}

## Tab 1

Foo

## Tab 2

Bar

## Tab 3

Baz

:::

## Figures {#sec-figures}

Figure [@fig-complex] is an example plot with multiple lines and a legend.

```{r}
#| label: fig-complex
#| fig-cap: "An **example** plot"
#| fig-alt: "A plot showing multiple lines and a legend."
#| fig-width: 8
#| fig-height: 5

library(ggplot2)

data <- data.frame(
  x = 1:10,
  y1 = 1:10,
  y2 = 10:1
)
ggplot(data, aes(x = x)) +
  geom_line(aes(y = y1, color = "Line 1")) +
  geom_line(aes(y = y2, color = "Line 2")) +
  labs(x = "X", y = "Y") +
  theme_minimal()
```

## Tables

Table [@tbl-complex] is a complex table with multiple columns and a caption.

```{r}
#| label: tbl-complex
#| tbl-cap: "An **example** table"
#| tbl-colwidths: [15,35,25,25]

library(knitr)

data <- data.frame(
  Category = c("A", "B", "C", "D"),
  Description = c("Longer description for A", "Description for B", "Short description", "Another longer description for D"),
  Value1 = c(12.345, 6.789, 1.234, 9.876),
  Value2 = c(100, 25, 500, 75)
)

kable(data, "pipe", align = c("l", "l", "r", "r"))
```

## Mermaid Diagrams

Figure [@fig-mermaid] is a simple flowchart created using Mermaid.

```{mermaid}
%%| fig-cap: "An **example** mermaid diagram"
%%| label: fig-mermaid
graph LR
    A[Start] --> B{Decision};
    B -- Yes --> C[Process 1];
    B -- No --> D[Process 2];
    C --> E[End];
    D --> E;
```

## Code Blocks

### Code Block (No Execution)

```python
# This is a Python code block, but it won't be executed.
def greet(name):
  print(f"Hello, {name}!")

greet("World")
```

### Code Block (With Execution)

```{r}
# This R code block will be executed.
x <- 10
y <- 5
print(x + y)
```

## Comment

This section should be empty, other than this sentence.

<!-- This is a comment. -->

## References

Various references are tested here:

* Figure: [@fig-complex]

* Table: [@tbl-complex]

* Section: [@sec-figures]

* Citation: [@luecken2021neurips]

* Citation with multiple authors: [@luecken2021neurips; @cannoodt2021viashfromscripts]

* Citation with doi: [@10.1101/2023.11.28.568918]

* Footnote: [^footnote-example]

* URL: [OpenProblems](https://openproblems.bio)

[^footnote-example]: This is a footnote.
